Twisted 11-dimensional supergravity

### 2021-10-20 intro.tex

\begin{center}
\begin{tikzcd}[row sep=large]
                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
 \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                         &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &                                                                                                
\end{tikzcd}
\end{center}
\label{diagram}

>>>>

\begin{center}
\begin{tikzcd}[row sep=large]
                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" description, pos=.5] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
 \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"]\arrow[rr, rightsquigarrow, bend right=25, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering minimal twist of type I}  &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                         &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &                                                                                                
\end{tikzcd}
\end{center}
\label{diagram}
